Placeholder Title... Something About Delegating Quantum Computations

### 2019-09-23 longoutput.tex
Change Chernoff bound variables

	Note that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=\pm1$. Let $p$ be the probability that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$.

	$$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]=-p+(1-p)$$
	\begin{align*}
		\Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
		&=\frac{1}{2}-\Omega\left(\frac{1}{\poly(T)}\right)\braket{\phi|H|\phi}
	\end{align*}

@@

\begin{theorem}
	Let $H$ be a local Hamiltonian with the following properties: TODO $\mathcal{G}_{XZ}$???
	\begin{itemize}
		\item has $t$ terms
		\item acts on $q$ qubits
		\item Ground state $0$...?
		\item Something something $\frac{3}{4}$?
	\end{itemize}
	Then, with the input, if honest is $n=O(\poly(t))$... TODO
\end{theorem}
\begin{proof}
	Let $\set{\ket{\phi_1}, \ket{\phi_2},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$. Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Omega(\frac{1}{\poly(t)})=p'$ for $i\ne1$. We now decompose the input in this basis.

	Fix $\frac{1}{2}<B<p'$. Consider the Chernoff bound.

	Let $\mathcal{I}=\mathbb{Z}_q^n$ be the collection of possible multi-indices. That is, we decompose the input as
	$$\sum_{J\in\mathcal{I}}\alpha_J\ket{\phi_J}$$

	We partition the multi-indices into three types.
	$$\mathcal{I}_1=\set{(1,1,\ldots,1)}$$
	$$\mathcal{I}_3=\set{(j_1, j_2,\ldots,j_n):\abs{\set{j_k=1}}\leq B}$$
	$$\mathcal{I}_2=\mathcal{I}\setminus\mathcal{I}_1\setminus\mathcal{I}_3$$

	Then we can write the input (?) as follows.
	$$\alpha\ket{\phi_1^{\otimes n}}+\sum_{J\in\mathcal{I}_2}\beta_J\ket{\phi_J}+\sum_{J\in\mathcal{I}_3}\gamma_J\ket{\phi_J}$$
	$$b=\sum_{J\in\mathcal{I}_2}\beta_J\overline{\beta_J}$$
	$$c=\sum_{J\in\mathcal{I}_3}\gamma_J\overline{\gamma_J}$$

>>>>

	Note that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=\pm1$. Let $p$ be the probability that $\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}=-1$.
$$\Rightarrow \frac{1}{D}\braket{\phi|H|\phi}=\E_{\widetilde{S}}[\sgn(d_{\widetilde{S}})\lambda_{\widetilde{S}}]=-p+(1-p)$$
	\begin{align*}
		\Rightarrow p&=\frac{1}{2}-\frac{1}{2D}\braket{\phi|H|\phi}\\
		&=\frac{1}{2}-\Omega\left(\frac{1}{\poly(T)}\right)\braket{\phi|H|\phi}
	\end{align*}

@@

\begin{theorem}
	Let $H$ be a local Hamiltonian with the following properties: TODO $\mathcal{G}_{XZ}$???
	\begin{itemize}
		\item has $t$ terms
		\item acts on $q$ qubits
		\item Ground state $0$...?
		\item Something something $\frac{3}{4}$?
	\end{itemize}
	Then, with the input, if honest is $n=O(\poly(t))$... TODO
\end{theorem}
\begin{proof}
	Let $\set{\ket{\phi_1}, \ket{\phi_2},\ldots,\ket{\phi_q}}$ be the eigenbasis of $H$. Now apply \autoref{ThmXZCheck} to get an algorithm that accepts $\ket{\phi_1}$ with probability $\frac{1}{2}$ and $\ket{\phi_i}$ with probability $\frac{1}{2}-\Delta$ for $i\ne1$, where $\Delta=\Omega\left(\frac{1}{\poly(t)}\right)$. We now decompose the input in this basis. Let $\mathcal{I}=\mathbb{Z}_q^n$ be the collection of possible multi-indices.
	$$\sum_{J\in\mathcal{I}}\alpha_J\ket{\phi_J}$$
	Fix $\delta<2\Delta$ and partition the multi-indices into three types.
	$$\mathcal{I}_1=\set{(1,1,\ldots,1)}$$
	$$\mathcal{I}_3=\set{(j_1, j_2,\ldots,j_n):\abs{\set{j_k=1}}\leq 2\delta n}$$
	$$\mathcal{I}_2=\mathcal{I}\setminus\mathcal{I}_1\setminus\mathcal{I}_3$$

	Apply Chernoff bound to $\frac{1}{2}-\delta$. There is overwhelming probability that...
	By Chernoff bound, there is overwhelming probability that...  Then we can write the input (?) as follows.
	$$\alpha\ket{\phi_1^{\otimes n}}+\sum_{J\in\mathcal{I}_2}\beta_J\ket{\phi_J}+\sum_{J\in\mathcal{I}_3}\gamma_J\ket{\phi_J}$$
	$$b=\sum_{J\in\mathcal{I}_2}\beta_J\overline{\beta_J}$$
	$$c=\sum_{J\in\mathcal{I}_3}\gamma_J\overline{\gamma_J}$$
